%!TeX program = pdflatex

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{microtype}

% Custom font
\usepackage{noto-mono}
\usepackage{inter}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{Black}{RGB}{0, 0, 0}
\definecolor{Accent}{RGB}{63, 103, 151}

% Sections formatting
\titleformat{\section}
{\vspace{-4pt}\raggedright\footnotesize}{}{0em}{}
[\color{Black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------%
% Custom commands

\newcommand{\fwRegular}[1]{{\sffamily #1\normalfont}}
\newcommand{\fwBlack}[1]{{\interheavy #1\normalfont}}
\newcommand{\fwBold}[1]{{\sffamily\textbf{#1}\normalfont}}
\newcommand{\fwSemiBold}[1]{{\intersemibold #1\normalfont}}
\newcommand{\fwExtraBold}[1]{{\interextrabold #1\normalfont}}
\newcommand{\mono}[1]{{\notomono #1\normalfont}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{0pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \small\fwBold{\MakeUppercase{\textls[20]{#1}}} & \scriptsize\MakeUppercase{#2} \\
      \footnotesize\textcolor{Accent}{\fwExtraBold{\MakeUppercase{\textls[20]{#3}}}}{\MakeUppercase{#4}} & \scriptsize\MakeUppercase{#5} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \fwBold{\MakeUppercase{\small\textls[20]{#1}}} -- \fwRegular{\footnotesize#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.10in, label={
    \color{white}-
}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in, label={-}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand{\seticon}[1]{\textcolor{Black}{\csname #1\endcsname}}


%----------CV STARTS HERE----------%
\begin{document}

%----------HEADING----------%
\fwBlack{\Huge\textls[100]{ANSELM\hspace{0.4em}JOSEPH}}\hspace*{1cm} \\ \vspace{5pt}
\fwBlack{\Large\textcolor{Accent}{\textls[100]{FULL\hspace{0.43em}STACK\hspace{0.43em}DEVELOPER}}} \\ \vspace{5pt}
\href{tel:+1-872-258-5803}{\small{\mono{+1\hspace{0.2em}(872)\hspace{0.2em}258-5803}}}
\hspace{0.43em}•\hspace{0.43em}\href{mailto:ajoseph17@hawk.iit.edu}{\small{\mono{ajoseph17@hawk.iit.edu}}}
\hspace{0.43em}•\hspace{0.43em}\href{https://www.linkedin.com/in/anselmj}{\small{\mono{linkedin.com/in/anselmj}}}
\hspace{0.43em}•\hspace{0.43em}\href{https://an23lm.github.io}{\small{\mono{an23lm.github.io}}} \\ \vspace{10pt}
\small{Full Stack Developer with 5+ years of experience in backend, web, and mobile applications. Master's in Computer Engineering with focus on Machine Learning. Experienced with React, React Native, Java, Node.js, MySQL, and MongoDB.}

%-----------EXPERIENCE-----------%
\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart

    \resumeSubheading
    {MOLEX}{Bangalore, India}
    {Software Engineer}{}{Dec 2019 -- Aug 2022}
    \resumeItemListStart
        \resumeItem{Owned Identity and Access Management (IAM) microservice built using Spring Boot and MongoDB, streamlined user authentication and authorization processes, reducing API development time by 10\% and enhancing security.}
        \resumeItem{Developed middleware to ingest and aggregate real-time data using Python, AWS; improving ingestion rate by 17\%.}
        \resumeItem{Improved digitization pipeline's efficiency by 70\% for terabytes of blueprints built on GCP, Python, Pillow, and Solr.}
    \resumeItemListEnd
    
    \resumeSubheading
    {CBREX Technologies}{Bangalore, India}
    {Product Engineer 1}{}{Aug 2017 -- Dec 2019}
    \resumeItemListStart
        \resumeItem{Refactored website and mobile app to use React and provide excellent UX, improving user engagement by 33\%.}
        \resumeItem{Created 2 JavaScript libraries, reducing redundant code by 20\% and improving UX and customer satisfaction.}
        \resumeItem{Communicated technical subjects to stakeholders and created actionable tasks, reducing delivery time of features.}
        \resumeItem{Contributed to adoption of Agile Methodologies and CI/CD, utilizing Jira and Jenkins, improving productivity by 30\%.}
        \resumeItem{Optimized MySQL queries and implemented API caching using Redis with Spring Boot, reducing load times by 44\%.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------%
\section{EDUCATION}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Illinois Institute of Technology}{Chicago, IL}
    {Masters in Computer Engineering}{, 3.9 GPA}{Expected May 2024}
    \resumeItemListStart
        \resumeItem{\textbf{Focus:}  Probability \& Statistics in CS, Machine Learning, and Artificial Intelligence.}
    \resumeItemListEnd

    \resumeSubheading
    {New Horizon College of Engineering}{Bangalore, India}
    {Bachelors in Computer Science and Engineering}{}{August 2013 -- May 2017}
    \resumeItemListStart
        \resumeItem{\textbf{Focus:}  Advanced Data Structures and Algorithms.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROJECTS-----------%
\section{ENTREPRENEURIAL EXPERIENCE}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {Dog Leads} {React.js, Next.js, Typescript, AWS, Machine Learning} {}
    \resumeItemListStart
        \resumeItem{Created a platform to generate leads for businesses using Artificial Intelligence.}
        \resumeItem{Implemented a recommendation system using collaborative filtering, increasing user engagement by 40\%.}
    \resumeItemListEnd

    \resumeProjectHeading
    {Earthen Shade} {React.js, Next.js, Vercel, Firebase, GCP, Typescript, Tailwind CSS} {}
    \resumeItemListStart
        \resumeItem {Designed and developed an e-commerce platform, finding balance between technical robustness and business impact, iterating with feedback from stakeholders and customers.}
        \resumeItem{Implemented a real-time chat feature using WebSocket and Socket.io, enhancing user engagement and reducing response time by 20\%.}
    \resumeItemListEnd

    \resumeProjectHeading
    {NoBias Investing} {React Native, Typescript, Swift, Java, GitLab CI/CD} {}
    \resumeItemListStart
        \resumeItem{Balanced between UX and performance on information-rich screens through a process of continuous improvement.}
        \resumeItem{Widespread device compatibility was prioritized and ensured reliability and responsiveness on low-end networks.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------%
\section{SKILLS}
    \begin{itemize}[leftmargin=0.10in, label={}]
	\small{\item{
        \fwSemiBold{Languages}{: JavaScript, TypeScript, Python, Java, Swift, Kotlin, Go.} \\
		\fwSemiBold{Frontend Technologies}{: React, React Native, SwiftUI, HTML, CSS, Tailwind CSS, Bootstrap.} \\
		\fwSemiBold{Backend Technologies}{: Google Cloud, Firebase, AWS, Node.js, Next.js, Spring Boot, Flask, MongoDB, Firestore, MySQL, Redis, Docker.} \\
		\fwSemiBold{Concepts}{: Operating System, Object Oriented Programming, Functional Programming, Caching, Encryption, Decryption, Artificial Intelligence, Machine Learning, Neural Networks, REST API, SOAP API, Database Normalization, Agile Methodology, Cloud Computing, Payment Systems, Containerization, CI/CD, Sockets, Networking, Security.} \\
	}}
    \end{itemize}

%-------------------------------------------%
\end{document}