%-----------EXPERIENCE-----------%
\section{PROFESSIONAL EXPERIENCE}\vspace*{-4pt}

\resumeSubHeadingListStart
 
    \resumeSubheading
    {Retell AI}{San Carlos, CA}
    {Member of Technical Staff}{}{Feb 2026 -- current}
    \resumeItemListStart
        \resumeItem{Built and operated full-stack features for a Voice AI platform (React, TypeScript, Node.js), including prompt orchestration flows for voice agents and customer configuration experiences.}
        \resumeItem{Shipped customer dashboards and analytics for call outcomes and agent performance, enabling rapid iteration based on usage metrics and product feedback.}
        \resumeItem{Implemented telephony integrations and features including call routing/transfer and DTMF handling to support reliable conversation workflows.}
        \resumeItem{Improved backend performance and reliability via query optimization, caching, and async jobs; owned designs, deployments, monitoring, and production issue resolution.}
    \resumeItemListEnd

    \resumeSubheading
    {Agilisium Consulting}{Chicago, IL}
    {Universal Music Group - Senior Application Developer}{}{Aug 2024 -- Feb 2026}
    \resumeItemListStart
        \resumeItem{Built features for Consumer Marketing Technologies (CMT) platform which perform at scale, serving millions of DAU, using Firebase Realtime Database, Google Cloud Functions, Google Big Query, Node.js, and React.}
        \resumeItem{Provide timely support and critical bug fixes for business stakeholders, prepare and ensure all systems are operational for high volume requests during large events.}
        \resumeItem{Optimized databases based on frequently queried data to result in an avg 40\% faster improvement in API response times.}
        \resumeItem{Write and maintain scripts to generate reports, automate tasks, migrate between services such as Lytics and Dotdigital.}
    \resumeItemListEnd

    \resumeSubheading
    {MOLEX}{Bangalore, India}
    {Software Engineer}{}{Dec 2019 -- Aug 2022}
    \resumeItemListStart
        \resumeItem{Owned Identity and Access Management (IAM) microservice built using Java, Spring Boot, and MongoDB, streamlined user authentication and authorization processes, reducing API development time by 10\% and enhancing security.}
        \resumeItem{Developed middleware to aggregate real-time data using Python, Kafka, AWS; improving ingestion rate by 17\%.}
        \resumeItem{Initiated push to improve code quality by implementing test driven development (TDD), code reviews, and static code analysis using JaCoCo, SonarQube, and JUnit, reducing QA testing time by 50\%.}
        \resumeItem{Improved digitization pipeline's efficiency by 70\% for terabytes of blueprints built on GCP, Python, Pillow, and Solr.}
    \resumeItemListEnd

    \resumeSubheading
    {CBREX Technologies}{Bangalore, India}
    {Product Engineer 1}{}{Aug 2017 -- Dec 2019}
    \resumeItemListStart
        \resumeItem{Refactored website to use Java, Spring Boot, React and Bootstrap to improve UX, increasing user engagement by 33\%.}
        \resumeItem{Created 2 JavaScript libraries, reducing redundant code by 20\% and improving UX and customer satisfaction.}
        \resumeItem{Communicated technical subjects to stakeholders and created actionable tasks, reducing delivery time of features.}
        \resumeItem{Contributed to adoption of Agile Methodologies and CI/CD, utilizing Jira and Jenkins, improving productivity by 30\%.}
        \resumeItem{Optimized MySQL queries and implemented API caching using Redis with Spring Boot, reducing load times by 44\%.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
